Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
add few ref.

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
``Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
 problem, because it doesn't look so easy.” Richard Feynman’s words are as true today as when he spoke them almost forty years ago.
 And it is this opinion of Feynman among others which prompted the enormous effort that has been expended on the development of quantum computing
 since then. The paper `Scalable Quantum Simulation of Molecular Energies' by O’Malley et al. is evidence of just how far the technology
  has come in this time, and indicates what we might expect from superconducting quantum computing technologies in the future.

@@

The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition, or simultaneous combination, of
both a predetermined `0’ and a `1’ state. In paper by O’Malley et al., the quantum algorithms were run on superconducting qubits. These are a
physical realisation of quantum bits based upon what are known as superconducting quantum interference devices (SQUIDs), and they are used here
to find properties of the wavefunction of molecular Hydrogen.

>>>>

\begin{document}
\title{Case study of Scalable Quantum Simulation of Molecular Energies}
\author{Shuhao Yang, James Mills, Shanice St John}
\date{\today}
\maketitle
\section{Introduction}
``Nature isn't classical, dammit, and if you want to make a simulation of nature, you'd better make it quantum mechanical, and by golly it's a wonderful
 problem, because it doesn't look so easy.” Richard Feynman’s words are as true today as when he spoke them almost forty years ago.
 And it is this opinion of Feynman among others which prompted the enormous effort that has been expended on the development of quantum computing
 since then. The paper `Scalable Quantum Simulation of Molecular Energies' \cite{o2016scalable} by O’Malley et al. is evidence of just how far the technology
  has come in this time, and indicates what we might expect from superconducting quantum computing technologies in the future.

@@

The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition, or simultaneous combination, of
both a predetermined `0’ and a `1’ state. In paper \cite{o2016scalable} by O’Malley et al., the quantum algorithms were run on superconducting qubits. These are a
physical realisation of quantum bits based upon what are known as superconducting quantum interference devices (SQUIDs), and they are used here
to find properties of the wavefunction of molecular Hydrogen.
